The successful campaign of the DEAP-3600 experiment demonstrates the feasibility of multi-tonne-scale LAr detectors, including the development and use of ultra-high purity acrylic~\cite{amaudruzDesignConstructionDEAP36002019a} and novel techniques for achieving heavily suppressed Rn contamination. Thanks to its large size, DEAP-3600 also demonstrated the promise of large-scale LAr detector for searching for dark matter at the highest masses, up to the Planck scale~\cite{deapcollaborationFirstDirectDetection2022}.  DarkSide-50 demonstrated the sensitivity of a LAr TPC using Underground Argon (UAr), heavily depleted in $^{39}$Ar, to light dark matter with nuclear~\cite{darksidecollaborationLowMassDarkMatter2018} and electronic~\cite{thedarksidecollaborationConstraintsSubGeVDarkMatter2018} couplings. This is due in part to the relatively light argon nucleus and to the high degree of chemical purity achievable in LAr due to its cold temperature.  The DarkSide-LowMass experiment is now being planned to leverage these advantages to search for dark matter with cross sections down to the solar neutrino fog with an estimated tonne-year exposure of further-depleted UAr.

The DarkSide-20k (DS-20k) experiment of the multinational Global Argon Dark Matter Collaboration (GADMC) will search for dark matter using an UAr target instrumented as a dual-phase time projection chamber (TPC)~\cite{Aalseth:2018gq}.  The GADMC includes more than 400 scientists from over 60 institutions, mostly coming from the ArDM, DarkSide-50, DEAP-3600, MiniCLEAN, and XENON collaborations, and DS-20k will inherit successful elements from these experiments. These include the use of UAr, which DarkSide-50 demonstrated to have an $^{39}$Ar concentration at least 1400 times smaller than atmospheric argon~\cite{Agnes:2015gu,Agnes:2016fz,Agnes:2018ep}, and a radiopure acrylic structure, a technology pioneered by the DEAP-3600 experiment~\cite{Nantais:2013jp,Amaudruz:2018gr}.  The TPC is designed to take advantage of the favorable properties of liquid argon, including demonstrated electron recoil background discrimination power better than $10^8$~\cite{Adhikari:2021} and excellent chemical purity~\cite{Ajaj:2019jx,Ajaj:2019jk}, and operate with $<0.1$ background events within the 20.2~t fiducial volume over a ten year run, other than an expected ($3.2 \pm 0.6$) events from coherent neutrino scattering.  The DS-20k experimental apparatus consists of three nested detectors installed within a membrane cryostat nearly identical to the two existing ProtoDUNE cryostats~\cite{Abi:2020gv,Abi:2020hj,Abi:2020je}: the inner two-phase argon TPC, a neutron veto, and an outer muon veto. The apparatus will be located in Hall C of the Gran Sasso National Laboratory (LNGS). The DS-20k UAr target will be extracted by Urania~\cite{Aalseth:2018gq}, an argon extraction plant capable of extracting 330~kg/d of UAr, and purified with the Aria plant~\cite{Agnes:2021us}, a 350~m cryogenic distillation column designed to separate argon and other rare stable isotopes.  As illustrated in Fig.~\ref{fig:limitplot_SI}, DarkSide-20k experiment extends the cross section vs. mass range sensitivity in the search for dark matter to  $4.6\times 10^{-48}$\,cm$^2$ for a 90\% C.L. exclusion (and $1.5\times 10^{-47}$\,cm$^2$ at a $5\sigma$ discovery significance) for a 1\,TeV/$c^2$ WIMP, well beyond any current or presently funded experiment.  This will lead to either discovery, confirmation, or exclusion of the WIMP dark matter hypothesis down to the level where coherent scatters from atmospheric neutrinos become an irreducible background.  DarkSide-20k will also be sensitive to a galactic supernova neutrino burst originating anywhere in the Milky Way Galaxy~\cite{Agnes:2021ke}.

The ultimate objective of the GADMC is the construction of the Argo detector, which will have a 300~t fiducial mass and will push experimental sensitivity into the atmospheric neutrino fog.  The excellent electron recoil (ER) rejection possible in argon will eliminate backgrounds from solar neutrinos, which will extend the sensitivity of Argo beyond that of technologies with more limited ER discrimination.  Such a large detector would also have excellent sensitivity to a neutrino burst associated with a galactic supernova~\cite{Agnes:2021ke}.  If located at SNOLAB or at similar depth, Argo will also have the potential to observe CNO neutrinos for the first time and solve the Solar Metallicity Problem~\cite{Agnes:2020wd,Franco:2016ex}.  The further expansion of several technologies are critical for the success of Argo. The continued development and operation of Urania~\cite{Aalseth:2018gq} and Aria~\cite{Agnes:2021us} would enable 400~t of UAr to be extracted and purified over a period of about five years. Facilities for the long-term underground storage and assay of this argon are also needed. The Argo detector will be instrumented with more than 100~m$^2$ of photodetectors. This would be greatly simplified by the continued evolution of the large-area SiPM-based photosensors developed for DS-20k~\cite{DIncecco:2018hy,DIncecco:2018fx} into digital SiPMs, which would reduce the quantity of cables, significantly reduce noise, and decrease the background rate in the detector. Finally, all future detectors entering into the neutrino fog would benefit from improved atmospheric neutrino background modeling, which currently dominates the uncertainty on the experimental sensitivity.